PCA and UMAP

### 2021-09-29 App_Nonessential/PCA.Rmd
readded files because error

---
title: "SVM, K-NN"
author: "Scott Coffin"
date: "2/18/2021"
output: 
 html_document:
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 4
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE, echo = FALSE)
```
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load packages
library(tidyverse) #General everything
library(RColorBrewer)
library(ggplot2) #General plotting
library(ggrepel) #For adding text labels that repel away from data points
library(calecopal) #Color palette
library(shiny) #Runs shiny
library(shinythemes) #Shiny theme for the page
library(shinyWidgets) #Widgets
library(scales) #SSD - Use the percent format
library(reshape2) #Overview tab - melts bars together
library(ssdtools) #SSD package
library(DT) #Build HTML data tables
#library(plotly) #Make plots interactive
library(viridis) #Colors
library(scales) #To use "percent" function
library(tigerstats) #turns things into percents
library(ggbeeswarm) #plot all points
library(fitdistrplus, exclude = 'select') #alt SSD 
library(RColorBrewer) #colors
library(pheatmap) #pretty heat maps
library(rpart)  #for trees
#library(rattle)    # Fancy tree plot This is a difficult library to install (https://gist.github.com/zhiyzuo/a489ffdcc5da87f28f8589a55aa206dd) 
library(rpart.plot)             # Enhanced tree plots
library(RColorBrewer)       # Color selection for fancy tree plot
library(party)                  # Alternative decision tree algorithm
# library(partykit)               # Convert rpart object to BinaryTree
library(pROC)   #for ROC curves
library(uwot) #umap
library(ISLR)  #for the Carseat Data
library(lme4) #general linearized mixed model GLMM
library(quantregForest)
library(caret) #support vector machines
library(tidyverse)
library(tidymodels)
library(skimr)
library(sf)
library(ggspatial)
library(nhdplusTools)
library(patchwork)
library(Metrics)
library(gt)
library(randomForest)

# Attach Packages
library(kernlab)      # SVM methodology
library(e1071)        # SVM methodology
```
## Data import
```{r data import}
# Load finalized dataset.
aoc <- read_csv("AquaticOrganisms_Clean_final.csv", guess_max = 10000) %>% 
  mutate(ID = paste0("ID",row_number()))

@@

# Support Vector Machine
## Kitchen Sink
### Visualization

#### Support Vector Machine - Non-linear

Support Vector Classifiers are a subset of the group of classification structures known as Support Vector Machines. Support Vector Machines can construct classification boundaries that are nonlinear in shape. The options for classification structures using the svm() command from the e1071 package are linear, polynomial, radial, and sigmoid. Toobserve relationships of classifiers, we plot the data in two dimensions.

```{r}
# Plot data
multiVar %>% 
ggplot(aes(x = log(size.length.um.used.for.conversions), y = log(dose.mg.L.master), color = effect_f, shape = effect_f)) + 
  geom_point(size = 2) +
  scale_color_manual(values=c("#000000", "#FF0000")) +
  theme(legend.position = "none")
```
Notice that the data is not linearly separable, and furthermore, isn’t all clustered together in a single group. There are two sections of class 1 observations with a cluster of class 2 observations in between. To demonstrate the power of SVMs, we’ll take 100 random observations from the set and use them to construct our boundary. We set kernel = "radial" based on the shape of our data and plot the results.

```{r}
# set pseudorandom number generator
set.seed(123)
# sample training data
set.seed(4)
kitchenSink_split <- kitchenSink %>%
  initial_split(prop = 0.75, strata = polymer) # splits data into training and testing set.
kitchenSink_train <- training(kitchenSink_split)
kitchenSink_test <- testing(kitchenSink_split)
# Examine the environment to be sure # of observations looks like the 75/25 split. 3199:1066.
count_kitchenSink <- paste0('n = ',nrow(kitchenSink))
skim(kitchenSink)

subTrain <- kitchenSink_test %>% 
  dplyr::select(c(effect_f, dose.mg.L.master, size.length.um.used.for.conversions)) %>% 
  mutate_if(~is.numeric(.) && (.) > 0, log10)

#fit model
svmfit_kitchenSink <- svm(effect_f ~ ., 
                          data = subTrain, kernel = "radial", gamma = 1, cost = 1)
summary(svmfit_kitchenSink)
# plot classifier
plot(svmfit_kitchenSink, data = subTrain)
```
The same procedure can be run using the kernlab package, which has far more kernel options than the corresponding function in e1071. In addition to the four choices in e1071, this package allows use of a hyperbolic tangent, Laplacian, Bessel, Spline, String, or ANOVA RBF kernel. To fit this data, we set the cost to be the same as it was before, 1.
```{r}
# Fit radial-based SVM in kernlab
kernfit <- ksvm(effect_f ~ ., data = subTrain, type = "C-svc", kernel = 'rbfdot', C = 1, scaled = c())
# Plot training data
plot(kernfit, data = subTrain)
```

### Data Split
```{r}
#choose relevant predictors and log-transform
kitchenSink <- aoc_z %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(doi = as.character(doi)) %>% 
  dplyr::select(size_f,
                #doi, #need to split studies
                size.length.um.used.for.conversions, shape, polymer, particle.volume.um3, density.mg.um.3, organism.group, bio.org, treatments, effect_f, exposure.duration.d, exposure.route, lvl1_f, dose.mg.L.master) %>%
  # mutate_if(~is.numeric(.) && (.) > 0, log10) %>% 
 # mutate(effect_10 = case_when( #convert ordinal to numeric
 #     effect_f == "Y" ~ 1,
 #     effect_f == "N" ~ 0
 #   ))
drop_na() #drop missing

skim(kitchenSink)
```
#### Drop NA
```{r}
# Create calibration and validation splits with tidymodels initial_split() function.
set.seed(4)
kitchenSink_split <- kitchenSink %>%
  initial_split(prop = 0.75, strata = polymer) # splits data into training and testing set.
# default is 3/4ths split (but 75% training, 25% testing).
# Stratification (strata) = grouping training/testing sets by region, state, etc.
# Using the "strata" call ensures the number of data points in the training data is equivalent to the proportions in the original data set. (Strata below 10% of the total are pooled together.)

# Create a training data set with the training() function
# Pulls from training and testing sets created by initial_split()
kitchenSink_train <- training(kitchenSink_split)
kitchenSink_test <- testing(kitchenSink_split)
# Examine the environment to be sure # of observations looks like the 75/25 split. 3199:1066.

count_kitchenSink <- paste0('n = ',nrow(kitchenSink))

skim(kitchenSink)
```

#### Rough Fix NA
```{r}
#rough fix
kitchenSink_roughfix <- na.roughfix(kitchenSink)

# Create calibration and validation splits with tidymodels initial_split() function.
set.seed(4)
kitchenSink_split_roughfix <- kitchenSink_roughfix %>%
  initial_split(prop = 0.75, strata = polymer) # splits data into training and testing set.
# default is 3/4ths split (but 75% training, 25% testing).
# Stratification (strata) = grouping training/testing sets by region, state, etc.
# Using the "strata" call ensures the number of data points in the training data is equivalent to the proportions in the original data set. (Strata below 10% of the total are pooled together.)

# Create a training data set with the training() function
# Pulls from training and testing sets created by initial_split()
kitchenSink_train_roughfix <- training(kitchenSink_split_roughfix)
kitchenSink_test_roughfix <- testing(kitchenSink_split_roughfix)
# Examine the environment to be sure # of observations looks like the 75/25 split. 3199:1066.

count_roughfix <- paste0('n = ',nrow(kitchenSink_roughfix))

skim(kitchenSink_roughfix)
```

#### Multiple Imputation NA

The algorithm starts by imputing NAs using na.roughfix. Then randomForest is called with the completed data. The proximity matrix from the randomForest is used to update the imputation of the NAs. For continuous predictors, the imputed value is the weighted average of the non-missing obervations, where the weights are the proximities. For categorical predictors, the imputed value is the category with the largest average proximity. This process is iterated iter times.

Note: Imputation has not (yet) been implemented for the unsupervised case. Also, Breiman (2003) notes that the OOB estimate of error from randomForest tend to be optimistic when run on the data matrix with imputed values.
```{r}
# impute values
#drop NA's in response
kitchenSink_noNa <- kitchenSink %>% drop_na(effect_f)

#impute
set.seed(111)
kitchenSink_rfImpute <- rfImpute(data = kitchenSink_noNa, 
                                    effect_f ~., #response value, cannot contain NA's
                                    iter = 4,
                                    ntree =75)

# Create calibration and validation splits with tidymodels initial_split() function.
set.seed(4)
kitchenSink_split_imputed <- kitchenSink_rfImpute %>%
  initial_split(prop = 0.75, strata = polymer) # splits data into training and testing set.
# default is 3/4ths split (but 75% training, 25% testing).
# Stratification (strata) = grouping training/testing sets by region, state, etc.
# Using the "strata" call ensures the number of data points in the training data is equivalent to the proportions in the original data set. (Strata below 10% of the total are pooled together.)

# Create a training data set with the training() function
# Pulls from training and testing sets created by initial_split()
kitchenSink_train_imputed <- training(kitchenSink_split_imputed)
kitchenSink_test_imputed <- testing(kitchenSink_split_imputed)
# Examine the environment to be sure # of observations looks like the 75/25 split. 3199:1066.

count_imputed <- paste0('n = ',nrow(kitchenSink_rfImpute))

skim(kitchenSink_rfImpute)
```

### Train
#### Drop Na
```{r}
#examine train and test sets
dim(kitchenSink_train); dim(kitchenSink_test)
```

Before we train our model, we’ll first implement the trainControl() method. This will control all the computational overheads so that we can use the train() function provided by the caret package. The training method will train our data on different algorithms.

First, let’s focus on the traincontrol() method:

```{r}
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
# The trainControl() method here, is taking 3 parameters.
# The “method” parameter defines the resampling method, in this demo we’ll be using the repeatedcv or the repeated cross-validation method.
# The next parameter is the “number”, this basically holds the number of resampling iterations.
# The “repeats ” parameter contains the sets to compute for our repeated cross-validation. We are using setting number =10 and repeats =3
# This trainControl() method returns a list. We are going to pass this on our train() method.

svm_Linear <- train(effect_f ~., 
                    data = kitchenSink_train, 
                    method = "bayesglm", #Bayesian Model
                    trControl = trctrl, 
                    preProcess = c("center", "scale"), 
                    tuneLength = 10)
#The “preProcess” parameter is for preprocessing our training data.
# We are passing 2 values in our “pre-process” parameter “center” & “scale”. These two help for centering and scaling the data.
# After pre-processing, these convert our training data with mean value as approximately “0” and standard deviation as “1”. The “tuneLength” parameter holds an integer value. This is for tuning our algorithm.

svm_Linear
```
It’s a linear model therefore, it just tested at value “C” = 1.

Now, our model is trained with C value as 1. We are ready to predict classes for our test set. We can use predict() method.

The caret package provides predict() method for predicting results. We are passing 2 arguments. Its first parameter is our trained model and second parameter “newdata” holds our testing data frame. The predict() method returns a list, we are saving it in a test_pred variable.

```{r}
test_pred <- predict(svm_Linear, newdata = kitchenSink_test)
confusionMatrix(table(test_pred, kitchenSink_test$effect_f))
```

The output shows that our model accuracy for test set is %

By following the above procedure, we can build our svmLinear classifier.

We can also do some customization for selecting C value(Cost) in Linear classifier. This can be done by inputting values in grid search.

The next code snippet will show you, building & tuning of an SVM classifier with different values of C.

We are going to put some values of C using expand.grid() into “grid” dataframe. Next step is to use this dataframe for testing our classifier at specific C values. It needs to be put in train() method with tuneGrid parameter.

```{r}
grid <- expand.grid(C = c(0,0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2,5))
svm_Linear_Grid <- train(effect_f ~., data = kitchenSink_train, method = "svmLinear",
                         trControl = trctrl,
                         preProcess = c("center", "scale"),
                         tuneGrid = grid,
                         tuneLength = 10)
svm_Linear_Grid
plot(svm_Linear_Grid)
```
The above plot is showing that our classifier is giving best accuracy on C = 1.75. Let’s try to make predictions using this model for our test set.

```{r}
test_pred_grid <- predict(svm_Linear_Grid, newdata = kitchenSink_train)
confusionMatrix(table(test_pred_grid, kitchenSink_train$effect_f))
```

# ROC Curves

Prep for plotting.
```{r}

#### kitchenSink
kitchenSinkpredictions <- as.data.frame(predict(kitchenSinkrf, kitchenSink_test%>% dplyr::select(-effect_f), type = "prob"))
# predict class and then attach test class
kitchenSinkpredictions$predict <- names(kitchenSinkpredictions)[1:2][apply(kitchenSinkpredictions[,1:2], 1, which.max)]
kitchenSinkpredictions$observed <- kitchenSink_test$effect_f
head(kitchenSinkpredictions)

#### kitchenSink_roughfix_roughfix
kitchenSink_roughfixpredictions <- as.data.frame(predict(kitchenSink_roughfixrf, kitchenSink_roughfix_test%>% dplyr::select(-effect_f), type = "prob"))
# predict class and then attach test class
kitchenSink_roughfixpredictions$predict <- names(kitchenSink_roughfixpredictions)[1:2][apply(kitchenSink_roughfixpredictions[,1:2], 1, which.max)]
kitchenSinkpredictions$observed <- kitchenSink_test$effect_f
head(kitchenSinkpredictions)

###CHRONIC
chronicpredictions <- as.data.frame(predict(chronicrf, chronic_test %>% dplyr::select(-effect_f), type = "prob"))
# predict class and then attach test class
chronicpredictions$predict <- names(chronicpredictions)[1:2][apply(chronicpredictions[,1:2], 1, which.max)]
chronicpredictions$observed <- chronic_test$effect_f

####ACUTE
predictions <- as.data.frame(predict(acuterf, acute_test%>% dplyr::select(-effect_f), type = "prob"))
# predict class and then attach test class
predictions$predict <- names(predictions)[1:2][apply(predictions[,1:2], 1, which.max)]
predictions$observed <- acute_test$effect_f
head(predictions)

###nofilter
nofilterpredictions <- as.data.frame(predict(nofilterrf, nofilter_test%>% dplyr::select(-effect_f), type = "prob"))
# predict class and then attach test class
nofilterpredictions$predict <- names(nofilterpredictions)[1:2][apply(nofilterpredictions[,1:2], 1, which.max)]
nofilterpredictions$observed <- nofilter_test$effect_f

###nofilterOptimized
nofilter.optimizedpredictions <- as.data.frame(predict(myrf_optimized, multiVar_smkitchenSink_test %>%  dplyr::select(-effect_f), type = "prob"))
# predict class and then attach test class
nofilter.optimizedpredictions$predict <- names(nofilter.optimizedpredictions)[1:2][apply(nofilter.optimizedpredictions[,1:2], 1, which.max)]
nofilter.optimizedpredictions$observed <- multiVar_smkitchenSink_test$effect_f

###nofilterOptimizedImputed
nofilter.optimized.imputedpredictions <- as.data.frame(predict(myrf_optimized_imputed, multiVar_smkitchenSink_test_imputed %>%  dplyr::select(-effect_f), type = "prob"))
# predict class and then attach test class
nofilter.optimized.imputedpredictions$predict <- names(nofilter.optimized.imputedpredictions)[1:2][apply(nofilter.optimized.imputedpredictions[,1:2], 1, which.max)]
nofilter.optimized.imputedpredictions$observed <- multiVar_smkitchenSink_test_imputed$effect_f
```
Plot.
```{r}
require(ggdark)
# 1 ROC curve, yes vs no for acute
roc.acute <- roc(ifelse(predictions$observed=="Y", "Y", "N"), as.numeric(predictions$Y))

#chronic
roc.chronic <- roc(ifelse(chronicpredictions$observed=="Y", "Y", "N"), as.numeric(chronicpredictions$Y))
#kitchenSink
roc.kitchenSink <- roc(ifelse(kitchenSinkpredictions$observed=="Y", "Y", "N"), as.numeric(kitchenSinkpredictions$Y))

#nofilter
roc.nofilter <- roc(ifelse(nofilterpredictions$observed=="Y", "Y", "N"), as.numeric(nofilterpredictions$Y))

#no filter (optimized)
roc.nofilter.optimized <- roc(ifelse(nofilter.optimizedpredictions$observed=="Y", "Y", "N"), as.numeric(nofilter.optimizedpredictions$Y))

#no filter (optimized; imputed)
roc.nofilter.optimized.imputed <- roc(ifelse(nofilter.optimized.imputedpredictions$observed=="Y", "Y", "N"), as.numeric(nofilter.optimized.imputedpredictions$Y))

##make ROC curves

#kitchenSink
kitchenSinkROC <- ggroc(roc.kitchenSink, col = "yellow") + 
  labs(title = "Chronic and Acute",
       subtitle = paste0(accuracy_kitchenSink,', ',count_kitchenSink)) + 
  dark_theme_bw()

#acute
acuteROC <- ggroc(roc.acute, col = "green") + 
  labs(title = "Acute",
       subtitle = paste0(accuracy_acute,', ',count_acute)) + 
  dark_theme_bw()

#chronic
chronicROC <- ggroc(roc.chronic, col = "blue") + 
  labs(title = "Chronic",
       subtitle = paste0(accuracy_chronic,', ',count_chronic)) + #auto label
  dark_theme_bw()

#no filter
nofilterROC <- ggroc(roc.nofilter, col = "red3") + 
  labs(title = "Entire Dataset",
       subtitle = paste0(accuracy_nofilter,', ',count_nofilter)) + 
  dark_theme_bw()

#optimized (rough fix)
nofilteroptimizedROC <- ggroc(roc.nofilter.optimized, col = "orangered") + 
  labs(title = "Entire Dataset (optimized)",
       subtitle = paste0(accuracy_optimized,', ',count_optimized)) + 
  dark_theme_bw()

#optimized (multiple imputation)
nofilteroptimizedimputedROC <- ggroc(roc.nofilter.optimized.imputed, col = "orange") + 
  labs(title = "Entire Dataset (optimized; imputed)",
       subtitle = paste0(accuracy_optimized_imputed,', ',count_optimized_imputed)) + 
  dark_theme_bw()

#arrange together and print
require(gridExtra)
grid.arrange(nofilterROC, nofilteroptimizedROC, nofilteroptimizedimputedROC,kitchenSinkROC, acuteROC, chronicROC,
             ncol = 3)
```
ROC curves may also be visualized together
```{r}
require(pROC)
require(tidyverse)
require(ggdark)
require(ggsci)
ggroc(list(kitchenSink = roc.nofilter, optimized = roc.nofilter.optimized, optimized.imputed = roc.nofilter.optimized.imputed, organisms = roc.kitchenSink, acute = roc.acute, chronic = roc.chronic), aes = c("linetype", "color")) +
  labs(title = "ROC Curves for Aquatic Toxicity Random Forest",
       subtitle = "n = 4615",
       color = "Dataset",
       linetype = "Dataset") +
   scale_color_tron() +
  # theme_bw(base_size = 20)
 dark_theme_bw(base_size = 20)# +
 theme(plot.title.position = element_text(hjust = 0.5),
     plot.subtitle.position = element_text(hjust = 0.5))
```

>>>>

---
title: "PCA and UMAP"
author: "Scott Coffin"
date: "2/18/2021"
output: 
  html_document:
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 4
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE, echo = FALSE)
```
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load packages
library(tidyverse) #General everything
library(RColorBrewer)
library(ggplot2) #General plotting
library(ggrepel) #For adding text labels that repel away from data points
library(calecopal) #Color palette
library(shiny) #Runs shiny
library(shinythemes) #Shiny theme for the page
library(shinyWidgets) #Widgets
library(scales) #SSD - Use the percent format
library(reshape2) #Overview tab - melts bars together
library(ssdtools) #SSD package
library(DT) #Build HTML data tables
#library(plotly) #Make plots interactive
library(viridis) #Colors
library(scales) #To use "percent" function
library(tigerstats) #turns things into percents
library(ggbeeswarm) #plot all points
library(fitdistrplus, exclude = 'select') #alt SSD 
library(RColorBrewer) #colors
library(pheatmap) #pretty heat maps
library(rpart)  #for trees
#library(rattle)    # Fancy tree plot This is a difficult library to install (https://gist.github.com/zhiyzuo/a489ffdcc5da87f28f8589a55aa206dd) 
library(rpart.plot)             # Enhanced tree plots
library(RColorBrewer)       # Color selection for fancy tree plot
library(party)                  # Alternative decision tree algorithm
# library(partykit)               # Convert rpart object to BinaryTree
library(pROC)   #for ROC curves
library(uwot) #umap
library(ISLR)  #for the Carseat Data
library(lme4) #general linearized mixed model GLMM
library(quantregForest)
library(caret)
library(tidyverse)
library(tidymodels)
library(skimr)
library(sf)
library(ggspatial)
library(nhdplusTools)
library(patchwork)
library(Metrics)
library(gt)
library(randomForest)
```
## Data import
```{r data import}
# Load finalized dataset.
aoc <- read_csv("AquaticOrganisms_Clean_final.csv", guess_max = 10000) %>% 
  mutate(ID = paste0("ID",row_number()))

@@

# PCA

# UMAP

```{r}
require(uwot)
require(Rtsne)
require(vizier) #devtools::install_github("jlmelville/vizier")

# For some functions we need to strip out non-numeric columns and convert data to matrix
x2m <- function(X) {
  if (!methods::is(X, "matrix")) {
    m <- as.matrix(X[, which(vapply(X, is.numeric, logical(1)))])
  }
  else {m <- X} 
  m}

#choose values with most completeness
multiVar2 <- multiVar %>% 
  filter(!environment == "Terrestrial") %>% 
  dplyr::select(size_f, size.length.um.used.for.conversions, shape, polymer, particle.volume.um3, density.mg.um.3, organism.group, bio.org, treatments, effect, exposure.duration.d, exposure.route, lvl1_f, dose.mg.L.master) %>% 
  mutate_if(~is.numeric(.) && (.) > 0, log10) %>% 
  drop_na() #drop missing

#convert discrete variables to numeric
multiVar2[] <- data.matrix(multiVar2)

# build umap for small dataset (<10,000 points)
multiVar_map  <- umap(multiVar2, pca = 10)

# Remove duplicates for t-SNE
#multiVar2_noNa_dup <- multiVar2_noNa[-which(duplicated(x2m(multiVar2_noNa))), ]

#build t-SNE
#multiVar_tsne <- Rtsne::Rtsne(multiVar2_noNa_dup, perplexity = 15, initial_dims = 100, partical_pca = TRUE, exaggeration_factor = 4)

# Non-numeric columns are ignored, so in a lot of cases you can pass a data
# frame directly to umap
#iris_umap <- umap(iris, n_neighbors = 50, learning_rate = 0.5, init = "random")

#visualize umap
embed_img <- function(X, Y, k = 15, ...) {
  args <- list(...)
  args$coords <- Y
  args$x <- X

  do.call(vizier::embed_plot, args)
}

#plot
embed_img(multiVar2, multiVar_map, pc_axes = TRUE, equal_axes = TRUE, alpha_scale = 0.5, title = "Tox UMAP", cex = 1)
```

```{r}
#PCA
pca <- stats::prcomp(multiVar2[,-5], retx = TRUE, rank. = 2)
#build color pallete
my_colors = colorRampPalette(c("red", "yellow", "green"))(nrow(multiVar2))
#plot
embed_plot(pca$x, multiVar2$polymer, color_scheme = palette.colors(palette = "Okabe-Ito"), #turbo, #rainbow, #my_colors, 
           title = "Polymer PCA", alpha_scale = 0.5, equal_axes = TRUE)
```

```{r}
require(plotly)
#PCA for discrete variables
multiVar_discrete <- multiVar %>% 
  select(size.length.um.used.for.conversions, polymer, dose.mg.L.master, exposure.duration.d) %>% 
  drop_na %>% 
  mutate_if(~is.numeric(.) && (.) > 0, log10)

#buildPCA
pca_discrete <- stats::prcomp(multiVar_discrete[,-2], retx = TRUE, rank. = 2)

embed_plotly(pca_discrete$x, multiVar_discrete$polymer, color_scheme = palette.colors(palette = "Okabe-Ito"), 
           title = "Polymer PCA", alpha_scale = 0.5, equal_axes = TRUE,
           tooltip = paste("Polymer:", multiVar_discrete$polymer))
```
